Dependently Typed Languages in Statix

### 2023-04-20 pres-thesis/presentation.tex
More slides on core

\begin{frame}[fragile]{Background: What is Spoofax?}
SDF3, Statix and Stratego (and more)

\begin{figure}
	\includegraphics[width=0.32\linewidth]{img/semantics}
	\includegraphics[width=0.32\linewidth]{img/syntax}
	\includegraphics[width=0.32\linewidth]{img/transformation}
\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Background: What are Dependent Types?}
	Type checking requires evaluation
	\begin{exampleblock}{Example 1}
		\texttt{let T = if false then Int else Bool end;\\let b: T = true;}
	\end{exampleblock}
\end{frame}

@@

	\begin{figure}
		\centering
		\begin{exampleblock}{Equivalent Statix code} 
			\texttt{typeOfExpr (s, Let(x, e, b)) = bt :-\\
				\,\, typeOfExpr (s, e) == et, \\
				\,\, typeOfExpr (sPutSubst (s, x, (s, e)), b) == bt}
		\end{exampleblock}
	\end{figure}

@@

\begin{frame}[fragile]{Type Checking}
	\begin{block}{How do we use scopes?}
		A scope is used as a replacement for an environment and a context.\\
		One edge \verb|p|. One relation \texttt{name $\rightarrow$ NameEntry}, NameEntry is either:
		\begin{itemize}
			\item NType: Stores a type (Corresponds to a context)
			\item NSubst: Stores a substitution (Corresponds to an environment)
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}[fragile]{Type Checking: Requires Evaluation}
	\begin{exampleblock}{Example 1}
		\texttt{let T = if false then Int else Bool end;\\let b: T = true;}
	\end{exampleblock}
	\begin{block}{Evaluation relation} 
		\texttt{betaHeadReduce : scope * Expr -> scope * Expr} \\
		\texttt{betaReduce : scope * Expr -> Expr} \\
		\texttt{exectBetaEq : (scope * Expr) * (scope * Expr)}
	\end{block}
\end{frame}

>>>>

\begin{frame}[fragile]{Background: What is Spoofax?}
\begin{figure}
	\includegraphics[width=0.8\linewidth]{img/syntax}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Background: What is Spoofax?}
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{img/semantics}
	\end{figure}
\end{frame}

\begin{frame}[fragile]{Background: What is Spoofax?}
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{img/transformation}
	\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Background: What are Dependent Types?}
	Type checking requires evaluation
	\begin{exampleblock}{Example 1}
		\texttt{let T: Type = if false then Int else Bool end;\\let b: T = true;}
	\end{exampleblock}
\end{frame}

@@

	\begin{figure}
		\centering
		\begin{exampleblock}{Equivalent Statix code} 
			\texttt{typeOfExpr (s, Let(x, e, b)) = bt :-\\
				\,\, typeOfExpr (s, e) == et, \\
				\,\, typeOfExpr (sPutSubst (s, x, (s, e)), b) == bt}
		\end{exampleblock}
	\end{figure}
\end{frame}

\begin{frame}[fragile]{Type Checking: Environments \& Context}
	\begin{exampleblock}{Example}
		\texttt{let T: Type = Bool;\\
			$\backslash$b: T. ???
		}
	\end{exampleblock}

	\begin{block}{What information is needed?}
		\begin{enumerate}
			\item T = Bool (Stored in Environment)
			\item x : T (Stored in Context)
		\end{enumerate}
	\end{block}
\end{frame}

\begin{frame}[fragile]{Type Checking: Environments \& Context}
	\begin{block}{How do we use scopes?}
		A scope is used as a replacement for an environment and a context.\\
		\begin{itemize}
			\item One type of edge: \verb|p|.
			\item One type of relation: \verb|NameEntry|, which can be:
				\begin{itemize}
					\item NType: Stores a type (Corresponds to a context)
					\item NSubst: Stores a substitution (Corresponds to an environment)
				\end{itemize}
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}[fragile]{Type Checking: Requires Evaluation}
	\begin{exampleblock}{Example from earlier}
		\texttt{let T = if false then Int else Bool end;\\let b: T = true;}
	\end{exampleblock}
	\begin{block}{Evaluation relation} 
		\texttt{betaHeadReduce : scope * Expr -> scope * Expr} \\
		\texttt{betaReduce : scope * Expr -> Expr} \\
		\texttt{exectBetaEq : (scope * Expr) * (scope * Expr)}
	\end{block}
\end{frame}

\begin{frame}[fragile]{Type Checking: Requires Evaluation}
	\begin{figure}
		\includegraphics[width=0.9\linewidth]{screenshot001}
	\end{figure}

@@
